Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-09 paper.tex

\begin{displayquote}
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  Thomas Jefferson~\cite{barlow:wine}
\end{displayquote}
It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched. Needless to say, with every unregulated
system comes abuse and piracy is no exception. As a Christian, how should one approach
such a tool and how can it be utilized for the betterment of God's kingdom? In the paper
that follows, piracy will be analyzed through a number of lenses, culminating in a
Christian response to this issue. In doing so, the hope is that the reader attains a
fresh, wholistic understanding of the potential value of piracy.
% explain the definition of piracy that we're using for this paper:
% it's not just the act of downloading copyrighted content but it includes the tools that
% are used to accomplish this task.

>>>>

\begin{displayquote}
  \textins{T}hat ideas should freely spread from one to another over the globe,
  for the moral and mutual instruction of man, and improvement of his
  condition, seems to have been peculiarly and benevolently designed by nature,
  when she made them, like fire, expansible over all space, without lessening
  their density at any point, and like the air in which we breathe, move, and
  have our physical being, incapable of confinement or exclusive appropriation.
  Inventions then cannot, in nature, be a subject of property.
  Thomas Jefferson~\cite{barlow:wine}
\end{displayquote}
It is generally accepted that piracy is an illegal activity, but what is often overlooked
is the legitimate role that piracy plays in a variety of contexts. When it comes to
subverting oppressive regimes, for instance, the tools that piracy provides are
indispensable and for protecting the interests of consumers from predatory business
practices, the abilities of piracy are unmatched.

Needless to say, with every unregulated system comes abuse and piracy is no exception.
On top of that, piracy, on an individual level, is extremely difficult to combat because
of the immaterial nature of the items that would need to be protected. Ideas flow freely
between people especially when the Internet is involved, so stopping this flow becomes an
exponentially more difficult problem the more people have the restricted data. The ease
with which ideas propagate lead people like Thomas Jefferson to claim that they are
``incapable of confinement or exclusive appropriation.'' Consequently, two parties form:
those that support piracy for its free and open spread of all information and those that
see piracy as a threat to the further advancement of technology and ideas.
